Computer Science House By-Laws

### 2016-11-07 bylaws.tex
Add files via upload
Changed 50% to 60%

\bsection{Creation of Accounts}
Root Type Persons have the authority to manage user accounts for House systems. Before members may receive an account they must:
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of Computer Science House and Rochester Institute of Technology facilities.
	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations.
	\item An Introductory member who fails to meet the signature percentage requirement may be approved for an account by 50\% majority vote at a House Meeting.
	This vote may be initiated by an Introductory member by notifying the Evaluations director of their intent after the completion of their packet.
	The Evaluations director will conduct the vote during a subsequent House Meeting, as appropriate.
	This may occur only once per Introductory Evaluation Process.
\end{enumerate}

\bsection{Code of Conduct}
The Code of Conduct located at \href{https://github.com/ComputerScienceHouse/CodeOfConduct} is the canonical Code of Conduct for Computer Science House accounts.
\\* \\*
Members are bound to the Code of Conduct revision that they sign when initially creating their account. Members may sign a more recent revision of the Code of Conduct to update their agreement.
\bsubsection{Changes}
The following process is used for making changes to the Code of Conduct document.
\begin{enumerate}
	\item A Root Type Person drafts a change to the Code of Conduct and makes publicly available both the summary and difference file of the change.
	\item The change is proposed at a House Meeting and is discussed at the same House Meeting.
	\item The final proposal is presented at the next House Meeting and ballots are distributed for a Balloted House vote as described in \ref{Balloted Vote}.
\end{enumerate}
\end{document}

>>>>

\bsection{Creation of Accounts}
Root Type Persons have the authority to manage user accounts for House systems. Before members may receive an account they must:
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item Sign the Code of Conduct sheets pertaining to the responsible utilization of Computer Science House and Rochester Institute of Technology facilities.
	\item Obtain greater than or equal to 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations.
\end{enumerate}
\item An Introductory member who fails to meet the signature percentage requirement may be approved for an account by 60\% majority vote at a House Meeting.
 	This vote may be initiated by an Introductory member by notifying the Evaluations director of their intent after the completion of their packet.
 	The Evaluations director will conduct the vote during a subsequent House Meeting, as appropriate.
 	This may occur only once per Introductory Evaluation Process.\bsection{Code of Conduct}
The Code of Conduct located at \href{https://github.com/ComputerScienceHouse/CodeOfConduct} is the canonical Code of Conduct for Computer Science House accounts.
\\* \\*
Members are bound to the Code of Conduct revision that they sign when initially creating their account. Members may sign a more recent revision of the Code of Conduct to update their agreement.
\bsubsection{Changes}
The following process is used for making changes to the Code of Conduct document.
\begin{enumerate}
	\item A Root Type Person drafts a change to the Code of Conduct and makes publicly available both the summary and difference file of the change.
	\item The change is proposed at a House Meeting and is discussed at the same House Meeting.
	\item The final proposal is presented at the next House Meeting and ballots are distributed for a Balloted House vote as described in \ref{Balloted Vote}.
\end{enumerate}
\end{document}
